Proposal full title \\ Proposal Acronym

### 2001-10-11 drafts/IST/PartC.tex
add small part in C7.
svn path=/trunk/; revision=1530

\chapter*{C5. Management}
\addcontentsline{toc}{chapter}{C5. Management}
\textit{This section, not exceeding two pages, should describe how the Take-Up
Action will be managed, the decision making structures to be applied, the
communication flow within the consortium and the quality assurance measures
which will be implemented, and how legal and ethical obligations, for example
concerning encryption or security of personal data, will be met.
The clustering of Assesment project will allow effective co-ordination, early
agreement - between users and suppliers - on globally accepted assesment
metrics and on competitive specifications, the timely delivery of relevant and
measurable results of assesment and their dissemination to other users
worldwide.\\
Actions management of an action is linked to the management of the underlying
business case (target application, baseline project. Relations and dependencies
including the risks involved should also be described. Beging linked under a
Support Node or Cluster will require co-operation with other actions.}
\\ \\
to be written.
\chapter*{C6. Description of the consortium}
\addcontentsline{toc}{chapter}{C6. Description of the consortium}
\textit{One page description of the consortium stating whom the participants
are, what their roles and functions in the consortium are, and how they
complement each other.\\
Where subcontractors are involved they should be clearly identified, and the
scope and nature of their work needs to be justified}
\\ \\ not yet written
\chapter*{C7. Description of the participants}
\addcontentsline{toc}{chapter}{C7. Descriptions of the participants}
\textit{Short description of the participating organisations including (no more
than two pages per organisation):
The expertise and experience of the organisation,
Short CVs of the key persones to be involved indicating relevant exprerience,
expertise and involvement in other EC projects. (Each CV no more than 10
lines). \\
This section should include a brief description of the main business of the
proposer(s) (or consortium, if applicable), including their business motivation
for the proposed action, and the business relevance. \\
It should be clear from this section what the user's current practices are,
which improvements are introduced during the course of the action, and what the
required and expected business practice upon completion of the action is}.
\\ \\ 
%% ALCOVE DE
\section*{Daniel Riek - Alcove Deutschland CTO}
%% Need to be improved and must be shorter
Daniel Riek switched to GNU/Linux in late 1993 short after graduating
from school. In early 1997 during his studies of computing science at the
university of Bonn he founded the Linux service company ID-PRO together
with some friends. During the next years he worked as a developer and
engineer, later he served in the management area of ID-PRO. After ID-PRO
received a major venture capital financing, Daniel became the chairman
and speaker of the board of directors. There he was responsible for the
technical strategy, representation, the community and public relationship.
He also was, together with the companies CTO, responsible for the technical
support and the software development activities of the company.
Caused by the capital market crisis in late 2000 ID-PRO failed to acquire
new funds, that would have been necessary due to the venture capital driven
strategy. After a short rest Daniel joined Alcove to continue his work in
the Free Software business. Daniel is a strong supporter of the Free
Software Foundation Europe and is a member of the board of germany's Linux
vendors association Linux-Verband LIVE e.V.
Next contributors : Christian, Jaime.
\chapter*{C8. Economic development and scientific and technological prospects}
\addcontentsline{toc}{chapter}{C8. Economic development and scientific and
technological prospecs}
\textit{This section, which should not exceed three pages, should describe
plans for the dissemination and - if relevant - the exploitation of the results
for the consortium as a whole and for the individual participants in contrete
terms. \\
This section must include an explanation of the potential for - internal and
external - replication, redeployment and/or reuse of results of the action. It
should a) describe in detail how the anticipated results will be used
internally within the participating organisations and what decisions may be
taken upon successful completion of the action, and b) identify the business
communities, sharing the problem to be solved by the action and describe a plan
how the results achieved, benefits obtained and lessons learnt (including key
competencies acquired, deficiencies removed, lasting changes) will be
disseminated/communicated and transferred to those communities. \\
Given the real benefits of an action may only become apparent several months
after completion of the action, proposers should indicate expected benefits in
the longer term (including measures that will be taken to assess them)}
\\ \\
to be written
\end{document}

>>>>

\chapter*{C5. Management}
\addcontentsline{toc}{chapter}{C5. Management}
\textit{This section, not exceeding two pages, should describe how the Take-Up
Action will be managed, the decision making structures to be applied, the
communication flow within the consortium and the quality assurance measures
which will be implemented, and how legal and ethical obligations, for example
concerning encryption or security of personal data, will be met.
\\
The clustering of Assesment project will allow effective co-ordination, early
agreement - between users and suppliers - on globally accepted assesment
metrics and on competitive specifications, the timely delivery of relevant and
measurable results of assesment and their dissemination to other users
worldwide.\\
Actions management of an action is linked to the management of the underlying
business case (target application, baseline project. Relations and dependencies
including the risks involved should also be described. Beging linked under a
Support Node or Cluster will require co-operation with other actions.}
\\ \\
to be written.
\chapter*{C6. Description of the consortium}
\addcontentsline{toc}{chapter}{C6. Description of the consortium}
\textit{One page description of the consortium stating whom the participants
are, what their roles and functions in the consortium are, and how they
complement each other.\\
Where subcontractors are involved they should be clearly identified, and the
scope and nature of their work needs to be justified}
\\ \\ not yet written
\chapter*{C7. Description of the participants}
\addcontentsline{toc}{chapter}{C7. Descriptions of the participants}
\textit{Short description of the participating organisations including (no more
than two pages per organisation):
The expertise and experience of the organisation,
Short CVs of the key persones to be involved indicating relevant exprerience,
expertise and involvement in other EC projects. (Each CV no more than 10
lines). \\
This section should include a brief description of the main business of the
proposer(s) (or consortium, if applicable), including their business motivation
for the proposed action, and the business relevance. \\
It should be clear from this section what the user's current practices are,
which improvements are introduced during the course of the action, and what the
required and expected business practice upon completion of the action is}.
\\ \\ 
%% ALCOVE DE
\section*{Daniel Riek - Alcove Deutschland CTO}
%% Need to be improved and must be shorter
Daniel Riek switched to GNU/Linux in late 1993 short after graduating
from school. In early 1997 during his studies of computing science at the
university of Bonn he founded the Linux service company ID-PRO together
with some friends. During the next years he worked as a developer and
engineer, later he served in the management area of ID-PRO. After ID-PRO
received a major venture capital financing, Daniel became the chairman
and speaker of the board of directors. There he was responsible for the
technical strategy, representation, the community and public relationship.
He also was, together with the companies CTO, responsible for the technical
support and the software development activities of the company.
Caused by the capital market crisis in late 2000 ID-PRO failed to acquire
new funds, that would have been necessary due to the venture capital driven
strategy. After a short rest Daniel joined Alcove to continue his work in
the Free Software business. Daniel is a strong supporter of the Free
Software Foundation Europe and is a member of the board of germany's Linux
vendors association Linux-Verband LIVE e.V.
\section*{GET - groupe PeCoVall}
GET (I'll have the official presentation on friday).\\ 
The PeCoVall group is composed of 5 professors and researchers 
from the 3 institutions ENST, ENST Bretagne and INT, that provide high education
in telecommunication.

This group has been formed last year to set up a project under GPL on an hosting 
environment specialy designed for high education. 
The members of the group are much concerned with free/open software and during the 
last three years, they organised five conferences related to free/open software 
in their institutions. One member is also a Debian maintener.

The telecommunication background of the group, and the need of some common 
data between the three sites led them to start a reflexion on cooperative
exchange in hosting platforms.

\\
Next contributors :  Jaime.
\chapter*{C8. Economic development and scientific and technological prospects}
\addcontentsline{toc}{chapter}{C8. Economic development and scientific and
technological prospecs}
\textit{This section, which should not exceed three pages, should describe
plans for the dissemination and - if relevant - the exploitation of the results
for the consortium as a whole and for the individual participants in contrete
terms. \\
This section must include an explanation of the potential for - internal and
external - replication, redeployment and/or reuse of results of the action. It
should a) describe in detail how the anticipated results will be used
internally within the participating organisations and what decisions may be
taken upon successful completion of the action, and b) identify the business
communities, sharing the problem to be solved by the action and describe a plan
how the results achieved, benefits obtained and lessons learnt (including key
competencies acquired, deficiencies removed, lasting changes) will be
disseminated/communicated and transferred to those communities. \\
Given the real benefits of an action may only become apparent several months
after completion of the action, proposers should indicate expected benefits in
the longer term (including measures that will be taken to assess them)}
\\ \\
to be written
\end{document}
